---
title: "Fancy Presentation"
author: "Mike McLaughlin"
date: "February 13, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## My First Slide

###Mike's Website - Visits Per Day


```{r, comment="", eval=TRUE}
visitsFile <- read.delim("C:/2017/Blog/Data_Files/date_count.txt",header=TRUE,sep=",",comment.char = "")
visitsFile$monthYear <- as.Date(as.character(visitsFile$DateEx),"%m/%d/%Y")

 plot(visitsFile$Unique.Visits ~ visitsFile$monthYear, data=visitsFile)

```


##My Second Slide

###Sub ONe
####Sub Two
#####Sub Three??

***
No heading

##Bullets

-Bullet One
-Bullet Two
-Bullet Three

1. One
2. Two
3. Three
  a. x
  b. x2



## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r visitsperday, echo = TRUE}
summary(visitsFile)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

